Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2015-01-06 paper/main.tex
minor fixes

\ifdefined\fullversion
\begin{figure}
\begin{lstlisting}
${\color{blue}
  \mbox{logical state invariant }
  \{ nm = A(0) \} }$
i=1; m=a[0];
while (i < N) {
  if (a[i] > m) {
    @assert(nm > 0); nm--;@
    m = a[i], tick(1);
  } i++, tick(1);
}
\end{lstlisting}
\caption{Example of assisted bound derivation using logical state.
  We write $A(i)$ for
  $\#\{ k \mid i \le k \le N \land \forall\, 0\le j<k.\, a[j] < a[k]\}$.
  The bound derived is $|[0,N]| + |[0,nm]|$.
  }
\label{fig:xmplmax}
\end{figure}
\fi

@@

In this appendix we provide a non-exhaustive catalog of classes of
programs that can be automatically analyzed by our system.  For
simplicity, and to compare our analysis with existing tools, we use
tick statements to count the number of loop iterations and function
calls.  This is the only resource that can be measured by tools like
KoAT~\cite{BrockschmidtEFFG14} and LOOPUS~\cite{SinnZV14}.  Sometimes
we also use (negative) tick statements to discuss features such as
resource restitution.

@@

   \caption{Well-Known Algorithms}
  \label{fig:cat3}
\end{figure*}

@@

\pref{fig:cat3} shows well-known algorithms that can be automatically
analyzed in our framework.  Example \emph{Knuth-Morris-Pratt} shows
the search function of the Knuth-Morris-Pratt algorithm for string
search.  To derive a bound for this algorithm we have add an assertion
that indicates the bounds of the values that are stored in the array
\code{b}.  Using this information we derive a tight linear bound.

>>>>

\ifdefined\fullversion
\begin{figure}
\begin{lstlisting}
${\color{blue}
  \mbox{logical state invariant }
  \{ nm = A(0) \} }$
i=1; m=a[0];
while (i < N) {
  if (a[i] > m) {
    @assert(nm > 0); nm--;@
    m = a[i], tick(1);
  } i++, tick(1);
}
\end{lstlisting}
\caption{Example of assisted bound derivation using logical state.
  We write $A(i)$ for
  $\#\{ k \mid i \le k \le N \land \forall\, 0\le j<k.\, a[j] < a[k]\}$.
  The bound derived is $|[0,N]| + |[0,nm]|$.
  }
% \label{fig:xmplmax2}
\end{figure}
\fi

@@

In this appendix we provide a non-exhaustive catalog of classes of
programs that can be automatically analyzed by our system.  For
simplicity, and to compare our analysis with existing tools,
the examples are automatically instrumented with tick statements
to count the number of loop iterations and function calls.
This is the only resource that can be measured by tools like
KoAT~\cite{BrockschmidtEFFG14} and LOOPUS~\cite{SinnZV14}.  Sometimes
we use tick statements explicitely to discuss features such as
resource restitution.

@@

   \caption{Well-Known Algorithms}
  \label{fig:wknown}
\end{figure*}

@@

\pref{fig:wknown} shows well-known algorithms that can be automatically
analyzed in our framework.  Example \emph{Knuth-Morris-Pratt} shows
the search function of the Knuth-Morris-Pratt algorithm for string
search.  To derive a bound for this algorithm we have add an assertion
that indicates the bounds of the values that are stored in the array
\code{b}.  Using this information we derive a tight linear bound.
